Report

### 2021-12-16 report.Rmd
Update report.Rmd

---
title: "Report"
output: pdf_document
---

>>>>

---
title: "Report"
output: pdf_document
---
## Abstract
### Importance
In the United States, many state legislatures have enacted a range of laws limiting access to abortions.  These laws limit access to healthcare.

### Objectives
To replicate the analysis of the association of abortion restrictions on abortion rates conducted by Brown et al. (2020), to expand the analysis to a wider data set, and to extend the analysis to associations with maternal, fetal and infant mortality rates, as well as birth and fertility rates.

### Design and Particpants
Propensity score adjusted linear regression of county level data on abortion rates, and state level data on mortality and natality rates, using data from 2010.

### Exposures
In the replication, the exposure is a highly restrictive abortion legislation as defined by 3 out 4 common types of abortion restrictions.  For the extension, the exposure is the number of types of abortion legislation.

### Main Outcomes and Measures
In the replication and extension, county level abortion rates defined as abortions per 1,000 women per year.  In the extension, state level fetal mortality rates ****, infant mortality rates ****, maternal mortality rates ****, birth rates defined as number of live births per 1,000 people, and fertility rates defined as number of live births per 1,000 women per year.

### Results

### Conclusions and Relevance
